---
title: "Annex D: Robustness Checks for Microstates, DV=Freedom House Index"
author: "Winston Wee"
output: 
  html_document:
    df_print: paged
    pdf_document: default
  fontsize: 12pt
---

\vspace{5ex}

```{=html}
<style>
body{
text-align: justify
}
</style>
```

```{r, echo=FALSE, message=FALSE, tidy=TRUE, results='hide'}
rm(list=ls())
cat("\014")
getwd()
setwd("Replication Files")
load_packages=c("dplyr","miceadds","readxl","writexl","data.table","naniar","car","bestNormalize","broom",
                "sandwich","lmtest","plm","ggplot2","fixest","textreg","stargazer","pcse","mediation",
                "prais","stringr","interactions","tidyverse","sjPlot","plm","lme4","nlme",
                "olsrr","multiwayvcov","ivreg","ghibli","formatR")
suppressMessages(lapply(load_packages,require,character.only=TRUE))
rm(load_packages)
## Loading HT-specific Functions
source("06 panelAR_HT Functions.R") # for the AR(1) correction
source("05 Functions.R") # for amended Mediation functions
source("07 Panel Cluster Robust SE Mediation.R") # for amended Mediation functions

## Load required datasets
load("Subsetted Datasets.RData")

demeaned=grep("_demeaned$",colnames(sample.micro),value=TRUE)
panel.micro=sample.micro[,c("country","year",demeaned)]
colname_panel=colnames(panel.micro)
colname_panel=gsub("_demeaned","",colname_panel)
colnames(panel.micro)=colname_panel
rm(colname_panel,panel_dat,sample.VDem,sample.full,demeaned)
```

# Regression Tables

## Table D1: Relationship between Logged Population and Democracy (Freedom House Index)

```{r, echo=TRUE, tidy=TRUE, results="asis"}
ATE_none=lm(fh_total_reversed~ln_popn+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+as.factor(year),sample.micro)

ATE_none_fe=lm(fh_total_reversed~ln_popn+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),panel.micro)

mo1=lm(fh_total_reversed~ln_popn+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+as.factor(year),sample.micro) # Main Y model

mo1_fe=lm(fh_total_reversed~ln_popn+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),panel.micro)

mo1_interact=lm(fh_total_reversed~ln_popn*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+as.factor(year),sample.micro)

mo1_interact_fe=lm(fh_total_reversed~ln_popn*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),panel.micro)

final.mod=list(ATE_none,mo1,mo1_fe,mo1_interact)
final.se=list(sqrt(diag(vcovPL(ATE_none,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(mo1,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(mo1_fe,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(mo1_interact,cluster=~country+year,aggregate=FALSE))))

stargazer(final.mod,
          type="latex",
          header=F,
          title="Table D1: Relationship between Logged Population and Democracy (Freedom House Index)",
          dep.var.caption = "Freedom House Index (Reversed)",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=final.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes","Yes"),
                           c("Country FE","No","No","Yes","No")),
          column.labels=c("Exposure-Outcome, Pooled","Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)"),
          column.separate=c(1,1,1,1),
          covariate.labels=c("Population (Logged)","Military Participation Rate",
                             "Urbanisation (% of Population)","Per Capita GDP (Logged)",
                             "Government Expenditurre (% of GDP)","Foreign Aid Received (% of GNI)",
                             "Resource Dependence","Ethnic Fractionalization",
                             "Population <span>&#215;</span> Urbanization",
                             "MPR <span>&#215;</span> Urbanization"),
          notes.align="l")#,out="Final Annex Table/Table D1.html")

```

# Table D2: Relationship between Logged Population and Military Participation Rate (Table 4 in thesis)

```{r, echo=TRUE, tidy=TRUE, results="asis"}

em1=lm(milrate~ln_popn+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+as.factor(year),sample.micro) # Main M model

em1_fe=lm(milrate~ln_popn+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),panel.micro)

em2=lm(milrate~ln_popn*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+as.factor(year),sample.micro)

em2_fe=lm(milrate~ln_popn*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),panel.micro)

em.mod=list(em1,em1_fe,em2)
em.se=list(sqrt(diag(vcovPL(em1,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(em1_fe,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(em2,cluster=~country+year,aggregate=FALSE))))

stargazer(em.mod,
          type="latex",
          header=F,
          title="Microstates Sample, Exposure-Mediator Models",
          dep.var.caption = "Military Participation Rate",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=em.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes"),
                           c("Country FE","No","Yes","No")),
          column.labels=c("Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)","Panel FE (Interaction)"),
          column.separate=c(1,1,1,1),
          covariate.labels=c("Population (Logged)",
                             "Urbanisation (% of Population)","Per Capita GDP (Logged)",
                             "Government Expenditurre (% of GDP)","Foreign Aid Received (% of GNI)",
                             "Resource Dependence","Ethnic Fractionalization",
                             "Population <span>&#215;</span> Urbanization"),
          notes.align="l")#,out="Final Annex Table/Table D2.html")
```

# Causal Mediation Analysis

## Hypothesis 3: The long-term operation of coercive capacity
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed1=panel_mediate_vcovPL_fixed(model.m = em1, model.y = mo1,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE)
summary(modmed1)
plot(modmed1,main="Pooled OLS, Mediator = milrate, Without Interaction",col="red")
text(x=modmed1$tau.coef,y=1,labels=paste0(round(modmed1$tau.coef,5)),pos=3) # ATE
text(x=modmed1$z.avg,y=2,labels=paste0(round(modmed1$z.avg,5)),pos=3) # ADE
text(x=modmed1$d.avg,y=3,labels=paste0(round(modmed1$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```

## Hypothesis 3a: The short-term operation of coercive capacity
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed2=panel_mediate_vcovPL_fixed(model.m = em1_fe, model.y = mo1_fe,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE)
summary(modmed2)
plot(modmed2,main="Panel FE, Mediator = milrate, Without Interaction",col="red")
text(x=modmed2$tau.coef,y=1,labels=paste0(round(modmed2$tau.coef,5)),pos=3) # ATE
text(x=modmed2$z.avg,y=2,labels=paste0(round(modmed2$z.avg,5)),pos=3) # ADE
text(x=modmed2$d.avg,y=3,labels=paste0(round(modmed2$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```

## Hypothesis 3b: The conditional operation of coercive capacity
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed3=panel_mediate_vcovPL_fixed(model.m = em2, model.y = mo1_interact,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE)
summary(modmed3)
test.modmed(modmed3,
            covariates.1=list(prop_urban=mean(sample.micro$prop_urban)-sd(sample.micro$prop_urban)),
            covariates.2=list(prop_urban=mean(sample.micro$prop_urban)+sd(sample.micro$prop_urban)),
            sims=1000)
plot(modmed3,main="Pooled OLS, Mediator = milrate, With Interaction",col="red")
text(x=modmed3$tau.coef,y=1,labels=paste0(round(modmed3$tau.coef,5),'**'),pos=3) # ATE
text(x=modmed3$z.avg,y=2,labels=paste0(round(modmed3$z.avg,5),'*'),pos=3) # ADE
text(x=modmed3$d.avg,y=3,labels=paste0(round(modmed3$d.avg,5),'**'),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)

# Additional Mediations
modmed3.1=panel_mediate_vcovPL_fixed(model.m = em2, model.y = mo1_interact,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE,
                                  covariates = list(prop_urban=mean(sample.micro$prop_urban)-sd(sample.micro$prop_urban)))
summary(modmed3.1)

modmed3.2=panel_mediate_vcovPL_fixed(model.m = em2, model.y = mo1_interact,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE,
                                  covariates = list(prop_urban=mean(sample.micro$prop_urban)+sd(sample.micro$prop_urban)))
summary(modmed3.2)
plot(modmed3.1,main="Pooled OLS, Mediator = milrate, With Interaction (Less Urban)",col="blue")
text(x=modmed3.1$tau.coef,y=1,labels=paste0(round(modmed3.1$tau.coef,5),'***'),pos=3) # ATE
text(x=modmed3.1$z.avg,y=2,labels=paste0(round(modmed3.1$z.avg,5),'***'),pos=3) # ADE
text(x=modmed3.1$d.avg,y=3,labels=paste0(round(modmed3.1$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)

plot(modmed3.2,main="Pooled OLS, Mediator = milrate, With Interaction (More Urban)",col="red")
text(x=modmed3.2$tau.coef,y=1,labels=paste0(round(modmed3.2$tau.coef,5)),pos=3) # ATE
text(x=modmed3.2$z.avg,y=2,labels=paste0(round(modmed3.2$z.avg,5)),pos=3) # ADE
text(x=modmed3.2$d.avg,y=3,labels=paste0(round(modmed3.2$d.avg,5),'**'),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```