---
title: "Annex J: IV Regressions"
author: "Winston Wee"
output: 
  html_document:
    df_print: paged
    pdf_document: default
  fontsize: 12pt
---

\vspace{5ex}

```{=html}
<style>
body{
text-align: justify
}
</style>
```

```{r, echo=FALSE, message=FALSE, tidy=TRUE, results='hide'}
rm(list=ls())
cat("\014")
getwd()
setwd("Replication Files")
load_packages=c("dplyr","miceadds","readxl","writexl","data.table","naniar","car","bestNormalize","broom",
                "sandwich","lmtest","plm","ggplot2","fixest","textreg","stargazer","pcse","mediation",
                "prais","stringr","interactions","tidyverse","sjPlot","plm","lme4","nlme",
                "olsrr","multiwayvcov","ivreg","ghibli","formatR","abe","interplot")
suppressMessages(lapply(load_packages,require,character.only=TRUE))
rm(load_packages)
## Loading HT-specific Functions
source("06 panelAR_HT Functions.R") # for the AR(1) correction
source("05 Functions.R") # for amended Mediation functions
source("07 Panel Cluster Robust SE Mediation.R") # for amended Mediation functions
source("09 Driscoll-Kraay SE Mediation.R") # SCC for Mediation
source("10 TSLS Mediation.R") # Mediation TSLS

## Load required datasets
load("04 Subsetted Datasets.RData")

demeaned=grep("_demeaned$",colnames(sample.VDem),value=TRUE)
panel.VDem=sample.VDem[,c("country","year",demeaned)]
colname_panel=colnames(panel.VDem)
colname_panel=gsub("_demeaned","",colname_panel)
colnames(panel.VDem)=colname_panel
rm(colname_panel,panel_dat,sample.micro,demeaned)
psample.VDem=pdata.frame(sample.VDem,index=c("country","year"))
```

# IV Regression Tables

## Table G1: Two-Stage Least Squares Regression, Relationship between Logged Population and Participatory Democracy

```{r,echo=TRUE,tidy=TRUE,results='asis'}
# Mediator Outcome
ATE_none=ivreg(v2x_partipdem~prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=sample.VDem)

ATE_Client=ivreg(v2x_partipdem~v2xnp_client+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=sample.VDem)

ATE_milrate=ivreg(v2x_partipdem~milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=sample.VDem)

vdem.4a=ivreg(v2x_partipdem~v2xnp_client+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=sample.VDem)

vdem.4b=ivreg(v2x_partipdem~v2xnp_client+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=panel.VDem)

mo1=ivreg(v2x_partipdem~ln_popn*prop_urban+ln_popn+prop_urban+ln_gdppc+v2xnp_client*prop_urban+milrate*prop_urban+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|temperature_wb*prop_urban+ln_arable*prop_urban+ln_rain*prop_urban+prop_urban+v2xnp_client*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

mofe=ivreg(v2x_partipdem~ln_popn*prop_urban+ln_popn+prop_urban+ln_gdppc+v2xnp_client*prop_urban+milrate*prop_urban+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year)|temperature_wb*prop_urban+ln_arable*prop_urban+ln_rain*prop_urban+prop_urban+v2xnp_client*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year),data=panel.VDem)


final.mod=list(ATE_none,ATE_Client,ATE_milrate,vdem.4a,vdem.4b,mo1)
final.se=list(sqrt(diag(vcovPL(ATE_none,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(ATE_Client,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(ATE_milrate,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(vdem.4a,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(vdem.4b,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(mo1,cluster=~country+year,aggregate=FALSE))))

stargazer(final.mod,
          type="latex",
          header=FALSE,
          title="Table G1: Two-Stage Least Squares Regression, Relationship between Logged Population and Participatory Democracy",
          dep.var.caption = "Varieties of Democracy, Participatory Democracy",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=final.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes","Yes","Yes","Yes"),
                           c("Country FE","No","No","No","No","Yes","No"),
                           c("Weak Instruments (Population Logged)",round(summary(ATE_none)[["diagnostics"]][1,3],3),
                             round(summary(ATE_Client)[["diagnostics"]][1,3],3),round(summary(ATE_milrate)[["diagnostics"]][1,3],3),
                             round(summary(vdem.4a)[["diagnostics"]][1,3],3),round(summary(vdem.4b)[["diagnostics"]][1,3],3),
                             round(summary(mo1)[["diagnostics"]][1,3],3)),
                           c("Weak Instruments (Population times Urbanisation)",NA,NA,NA,NA,NA,
                             round(summary(mo1)[["diagnostics"]][2,3],3))),
          column.labels=c("Exposure-Outcome, Pooled","Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)","Panel FE (Interaction)"),
          column.separate=c(3,1,1,1),
          covariate.labels=c("Population (Logged)","Clientelism",
                             "Military Participation Rate","Urbanisation (% of Population)",
                             "Per Capita GDP (Logged)","Government Expenditurre (% of GDP)",
                             "Foreign Aid Received (% of GNI)","Resource Dependence",
                             "Ethnic Fractionalization","Islamic",
                             "Population $mathrm{times}$ Urbanization",
                             "Clientelism $mathrm{times}$ Urbanization",
                             "MPR $mathrm{times}$ Urbanization"),
          notes.align="l")
```

## Table G2: Two-Stage Least Squares Regression, Relationship between Logged Population and Military Participation Rate

```{r,echo=TRUE,tidy=TRUE,results='asis'}

#Exposure Mediator (Milrate)

vdem.6a=ivreg(milrate~v2xnp_client+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=sample.VDem)

vdem.6b=ivreg(milrate~v2xnp_client+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=panel.VDem)

em_milrate=ivreg(milrate~ln_popn*prop_urban+ln_popn+prop_urban+ln_gdppc+v2xnp_client*prop_urban+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|temperature_wb*prop_urban+ln_arable*prop_urban+ln_rain*prop_urban+prop_urban+v2xnp_client*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

emfe_milrate=ivreg(milrate~ln_popn*prop_urban+ln_popn+prop_urban+ln_gdppc+v2xnp_client*prop_urban+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year)|temperature_wb*prop_urban+ln_arable*prop_urban+ln_rain*prop_urban+prop_urban+v2xnp_client*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year),data=panel.VDem)

em.mod=list(vdem.6a,vdem.6b,em_milrate)

em.se=list(sqrt(diag(vcovPL(vdem.6a,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(vdem.6b,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(em_milrate,cluster=~country+year,aggregate=FALSE))))

stargazer(em.mod,
          type="latex",
          header=FALSE,
          title="Table G2: Two-Stage Least Squares Regression, Relationship between Logged Population and Military Participation Rate",
          dep.var.caption = "Military Participation Rate",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=em.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes"),c("Country FE","No","Yes","No"),
                           c("Weak Instruments (Population Logged)",round(summary(vdem.6a)[["diagnostics"]][1,3],3),
                             round(summary(vdem.6b)[["diagnostics"]][1,3],3),round(summary(em_milrate)[["diagnostics"]][1,3],3)),
                           c("Weak Instruments (Population times Urbanisation)","NA","NA",
                             round(summary(em_milrate)[["diagnostics"]][2,3],3))),
          column.labels=c("Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)","Panel FE (Interaction)"),
          column.separate=c(1,1,1),
          covariate.labels=c("Population (Logged)","Clientelism",
                             "Urbanisation (% of Population)",
                             "Per Capita GDP (Logged)","Government Expenditurre (% of GDP)",
                             "Foreign Aid Received (% of GNI)","Resource Dependence",
                             "Ethnic Fractionalization","Islamic",
                             "Population $mathrm{times}$ Urbanization",
                             "Clientelism $mathrm{times}$ Urbanization"),
          notes.align="l")
```

## Table G3: Two-Stage Least Squares Regression, Relationship between Logged Population and Clientelism

```{r,echo=TRUE,tidy=TRUE,results='asis'}

#Exposure Mediator (Clientelism)

vdem.8a=ivreg(v2xnp_client~milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=sample.VDem)

vdem.8b=ivreg(v2xnp_client~milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year)|ln_popn|temperature_wb+ln_arable+ln_rain,data=panel.VDem)

em_client=ivreg(v2xnp_client~ln_popn*prop_urban+ln_popn+prop_urban+ln_gdppc+milrate*prop_urban+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year)|temperature_wb*prop_urban+ln_arable*prop_urban+ln_rain*prop_urban+prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

emfe_client=ivreg(v2xnp_client~ln_popn*prop_urban+ln_popn+prop_urban+ln_gdppc+milrate*prop_urban+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year)|temperature_wb*prop_urban+ln_arable*prop_urban+ln_rain*prop_urban+prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+as.factor(country)+as.factor(year),data=panel.VDem)


em.mod=list(vdem.8a,vdem.8b,em_client)

em.se=list(sqrt(diag(vcovPL(vdem.8a,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(vdem.8b,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(em_client,cluster=~country+year,aggregate=FALSE))))

stargazer(em.mod,
          type="latex",
          header=FALSE,
          title="Table G3: Two-Stage Least Squares Regression, Relationship between Logged Population and Clientelism",
          dep.var.caption = "Clientelism",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=em.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes"),c("Country FE","No","Yes","No"),
                           c("Weak Instruments (Population Logged)",round(summary(vdem.8a)[["diagnostics"]][1,3],3),
                             round(summary(vdem.8b)[["diagnostics"]][1,3],3),round(summary(em_client)[["diagnostics"]][1,3],3)),
                           c("Weak Instruments (Population times Urbanisation)","NA","NA",
                             round(summary(em_client)[["diagnostics"]][2,3],3))),
          column.labels=c("Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)"),
          column.separate=c(1,1,1),
          covariate.labels=c("Population (Logged)",
                             "Military Participation Rate","Urbanisation (% of Population)",
                             "Per Capita GDP (Logged)","Government Expenditure (% of GDP)",
                             "Foreign Aid Received (% of GNI)","Resource Dependence",
                             "Ethnic Fractionalization","Islamic",
                             "Population $mathrm{times}$ Urbanization",
                             "MPR $mathrm{times}$ Urbanization"),
          notes.align="l")
```