---
title: "Annex B: Robustness Checks for V-Dem Sample, DV=Freedom House Index"
author: "Winston Wee"
output: 
  html_document:
    df_print: paged
    pdf_document: default
  fontsize: 12pt
---

\vspace{5ex}

```{=html}
<style>
body{
text-align: justify
}
</style>
```

```{r, echo=FALSE, message=FALSE, tidy=TRUE, results='hide'}
rm(list=ls())
cat("\014")
getwd()
setwd("Replication Files")
load_packages=c("dplyr","miceadds","readxl","writexl","data.table","naniar","car","bestNormalize","broom",
                "sandwich","lmtest","plm","ggplot2","fixest","textreg","stargazer","pcse","mediation",
                "prais","stringr","interactions","tidyverse","sjPlot","plm","lme4","nlme",
                "olsrr","multiwayvcov","ivreg","ghibli","formatR")
suppressMessages(lapply(load_packages,require,character.only=TRUE))
rm(load_packages)
## Loading HT-specific Functions
source("06 panelAR_HT Functions.R") # for the AR(1) correction
source("05 Functions.R") # for amended Mediation functions
source("07 Panel Cluster Robust SE Mediation.R") # for amended Mediation functions

## Load required datasets
load("Subsetted Datasets.RData")

demeaned=grep("_demeaned$",colnames(sample.VDem),value=TRUE)
panel.VDem=sample.VDem[,c("country","year",demeaned)]
colname_panel=colnames(panel.VDem)
colname_panel=gsub("_demeaned","",colname_panel)
colnames(panel.VDem)=colname_panel
rm(colname_panel,panel_dat,sample.micro,sample.full,demeaned)
```

# Regression Tables

## Table B1: Relationship between Logged Population and Democracy (Freedom House Index)

```{r,echo=TRUE,tidy=TRUE,results='asis'}
# Mediator Outcome
ATE_none=lm(fh_total_reversed~ln_popn+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

ATE_Client=lm(fh_total_reversed~ln_popn+v2xnp_client+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

ATE_milrate=lm(fh_total_reversed~ln_popn+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

vdem.4a=lm(fh_total_reversed~ln_popn+v2xnp_client+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

vdem.4b=lm(fh_total_reversed~ln_popn+v2xnp_client+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),data=panel.VDem)

mo1=lm(fh_total_reversed~ln_popn*prop_urban+v2xnp_client*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

mofe=lm(fh_total_reversed~ln_popn*prop_urban+v2xnp_client*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),data=panel.VDem)

final.mod=list(ATE_none,ATE_Client,ATE_milrate,vdem.4a,vdem.4b,mo1)
final.se=list(sqrt(diag(vcovPL(ATE_none,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(ATE_Client,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(ATE_milrate,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(vdem.4a,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(vdem.4b,cluster=~country+year,aggregate=FALSE))),
              sqrt(diag(vcovPL(mo1,cluster=~country+year,aggregate=FALSE))))

stargazer(final.mod,
          type="html",
          title="Table B1: Relationship between Logged Population and Democracy (Freedom House Index)",
          dep.var.caption = "Freedom House Index",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=final.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes","Yes","Yes","Yes"),
                           c("Country FE","No","No","No","No","Yes","No")),
          column.labels=c("Exposure-Outcome, Pooled","Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)","Panel FE (Interaction)"),
          column.separate=c(3,1,1,1),
          covariate.labels=c("Population (Logged)","Clientelism",
                             "Military Participation Rate","Urbanisation (% of Population)",
                             "Per Capita GDP (Logged)","Government Expenditurre (% of GDP)",
                             "Foreign Aid Received (% of GNI)","Resource Dependence",
                             "Ethnic Fractionalization","Islamic",
                             "Population <span>&#215;</span> Urbanization",
                             "Clientelism <span>&#215;</span> Urbanization",
                             "MPR <span>&#215;</span> Urbanization"),
          notes.align="l",
          out="Final Annex Table/Table B1.html")
```

## Table B2: Relationship between Logged Population and Military Participation Rate (Table 4 in thesis)

```{r,echo=TRUE,tidy=TRUE,results='asis'}

#Exposure Mediator (Milrate)

vdem.6a=lm(milrate~ln_popn+v2xnp_client+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

vdem.6b=lm(milrate~ln_popn+v2xnp_client+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),data=panel.VDem)

em_milrate=lm(milrate~ln_popn*prop_urban+v2xnp_client*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

emfe_milrate=lm(milrate~ln_popn*prop_urban+v2xnp_client*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),data=panel.VDem)

em.mod=list(vdem.6a,vdem.6b,em_milrate)

em.se=list(sqrt(diag(vcovPL(vdem.6a,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(vdem.6b,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(em_milrate,cluster=~country+year,aggregate=FALSE))))

stargazer(em.mod,
          type="html",
          title="Table B2: Relationship between Logged Population and Military Participation Rate (Table 4 in thesis)",
          dep.var.caption = "Military Participation Rate",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=em.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes","Yes"),c("Country FE","No","Yes","No","Yes")),
          column.labels=c("Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)","Panel FE (Interaction)"),
          column.separate=c(1,1,1,1),
          covariate.labels=c("Population (Logged)","Clientelism",
                             "Urbanisation (% of Population)",
                             "Per Capita GDP (Logged)","Government Expenditurre (% of GDP)",
                             "Foreign Aid Received (% of GNI)","Resource Dependence",
                             "Ethnic Fractionalization","Islamic",
                             "Population <span>&#215;</span> Urbanization",
                             "Clientelism <span>&#215;</span> Urbanization"),
          notes.align="l",
          out="Final Annex Table/Table B2.html")
```

## Table B3: Relationship between Logged Population and Clientelism (Table 3 in thesis)

```{r,echo=TRUE,tidy=TRUE,results='asis'}

#Exposure Mediator (Clientelism)

vdem.8a=lm(v2xnp_client~ln_popn+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

vdem.8b=lm(v2xnp_client~ln_popn+milrate+prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),data=panel.VDem)

em_client=lm(v2xnp_client~ln_popn*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+ethfrac_alesina2003+islamic+as.factor(year),data=sample.VDem)

emfe_client=lm(v2xnp_client~ln_popn*prop_urban+milrate*prop_urban+ln_gdppc+govexpend_ratio+total_odashare_oecd+resourcerent+country+as.factor(year),data=panel.VDem)


em.mod=list(vdem.8a,vdem.8b,em_client)

em.se=list(sqrt(diag(vcovPL(vdem.8a,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(vdem.8b,cluster=~country+year,aggregate=FALSE))),
           sqrt(diag(vcovPL(em_client,cluster=~country+year,aggregate=FALSE))))

stargazer(em.mod,
          type="html",
          title="Table B3: Relationship between Logged Population and Clientelism (Table 3 in thesis)",
          dep.var.caption = "Clientelism",
          digits=4,digits.extra=3,p.auto=T,t.auto=T,
          se=em.se,
          report="vc*sp",
          star.cutoffs=c(0.05,0.01,0.005),
          style="ajps",
          omit=c("year","country"),
          add.lines = list(c("Year FE","Yes","Yes","Yes"),c("Country FE","No","Yes","No")),
          column.labels=c("Pooled (No Interaction)","Panel FE (No Interaction)","Pooled (Interaction)"),
          column.separate=c(1,1,1),
          covariate.labels=c("Population (Logged)",
                             "Military Participation Rate","Urbanisation (% of Population)",
                             "Per Capita GDP (Logged)","Government Expenditurre (% of GDP)",
                             "Foreign Aid Received (% of GNI)","Resource Dependence",
                             "Ethnic Fractionalization","Islamic",
                             "Population <span>&#215;</span> Urbanization",
                             "MPR <span>&#215;</span> Urbanization"),
          notes.align="l",
          out="Final Annex Table/Table B3.html")
```

# Causal Mediation Analysis

## Hypothesis 2: The long-term operation of clientelism
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed1_client=panel_mediate_vcovPL_fixed(model.m = vdem.8a, model.y = vdem.4a,
                                          treat = "ln_popn", mediator = "v2xnp_client",
                                          sims = 1000, robustSE = TRUE)
summary(modmed1_client)
plot(modmed1_client,main="Pooled OLS, Mediator = v2xnp_client, Without Interaction",col="red")
text(x=modmed1_client$tau.coef,y=1,labels=paste0(round(modmed1_client$tau.coef,5)),pos=3) # ATE
text(x=modmed1_client$z.avg,y=2,labels=paste0(round(modmed1_client$z.avg,5)),pos=3) # ADE
text(x=modmed1_client$d.avg,y=3,labels=paste0(round(modmed1_client$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```

## Hypothesis 2a: The short-term-term operation of clientelism
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed2_client=panel_mediate_vcovPL_fixed(model.m = vdem.8b, model.y = vdem.4b,
                                          treat = "ln_popn", mediator = "v2xnp_client",
                                          sims = 1000, robustSE = TRUE)
summary(modmed2_client)
plot(modmed2_client,main="Panel FE, Mediator = v2xnp_client, Without Interaction",col="red")
text(x=modmed2_client$tau.coef,y=1,labels=paste0(round(modmed2_client$tau.coef,5)),pos=3) # ATE
text(x=modmed2_client$z.avg,y=2,labels=paste0(round(modmed2_client$z.avg,5),'**'),pos=3) # ADE
text(x=modmed2_client$d.avg,y=3,labels=paste0(round(modmed2_client$d.avg,5),'***'),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```

## Hypothesis 2b: The conditional operation of clientelism
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed4=panel_mediate_vcovPL_fixed(model.m = em_client, model.y = mo1,
                                  treat = "ln_popn", mediator = "v2xnp_client",
                                  sims = 1000, robustSE = TRUE)
summary(modmed4)
test.modmed(modmed4,
            covariates.1=list(prop_urban=mean(sample.VDem$prop_urban)-sd(sample.VDem$prop_urban)),
            covariates.2=list(prop_urban=mean(sample.VDem$prop_urban)+sd(sample.VDem$prop_urban)),
            sims=1000)
plot(modmed4,main="Pooled OLS, Mediator = v2xnp_client, With Interaction",col="red")
text(x=modmed4$tau.coef,y=1,labels=paste0(round(modmed4$tau.coef,5)),pos=3) # ATE
text(x=modmed4$z.avg,y=2,labels=paste0(round(modmed4$z.avg,5)),pos=3) # ADE
text(x=modmed4$d.avg,y=3,labels=paste0(round(modmed4$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)

# Additional Mediations
## Less Urban Countries
modmed4.1=panel_mediate_vcovPL_fixed(model.m = em_client, model.y = mo1,
                                  treat = "ln_popn", mediator = "v2xnp_client",
                                  sims = 1000, robustSE = TRUE,
                                  covariates = list(prop_urban=mean(sample.VDem$prop_urban)-sd(sample.VDem$prop_urban)))
summary(modmed4.1)

## More Urban Countries
modmed4.2=panel_mediate_vcovPL_fixed(model.m = em_client, model.y = mo1,
                                  treat = "ln_popn", mediator = "v2xnp_client",
                                  sims = 1000, robustSE = TRUE,
                                  covariates = list(prop_urban=mean(sample.VDem$prop_urban)+sd(sample.VDem$prop_urban)))
summary(modmed4.2)

plot(modmed4.1,main="Pooled OLS, Mediator = v2xnp_client, With Interaction (Less Urban)",col="blue")
text(x=modmed4.1$tau.coef,y=1,labels=paste0(round(modmed4.1$tau.coef,5)),pos=3) # ATE
text(x=modmed4.1$z.avg,y=2,labels=paste0(round(modmed4.1$z.avg,5)),pos=3) # ADE
text(x=modmed4.1$d.avg,y=3,labels=paste0(round(modmed4.1$d.avg,5),'**'),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)

plot(modmed4.2,main="Pooled OLS, Mediator = v2xnp_client, With Interaction (More Urban)",col="red")
text(x=modmed4.2$tau.coef,y=1,labels=paste0(round(modmed4.2$tau.coef,5)),pos=3) # ATE
text(x=modmed4.2$z.avg,y=2,labels=paste0(round(modmed4.2$z.avg,5)),pos=3) # ADE
text(x=modmed4.2$d.avg,y=3,labels=paste0(round(modmed4.2$d.avg,5),'**'),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```

## Hypothesis 3: The long-term operation of coercive capacity
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed1_milrate=panel_mediate_vcovPL_fixed(model.m = vdem.6a, model.y = vdem.4a,
                                           treat = "ln_popn", mediator = "milrate",
                                           sims = 1000, robustSE = TRUE)
summary(modmed1_milrate)
plot(modmed1_milrate,main="Pooled OLS, Mediator = milrate, Without Interaction",col="red")
text(x=modmed1_milrate$tau.coef,y=1,labels=paste0(round(modmed1_milrate$tau.coef,5)),pos=3) # ATE
text(x=modmed1_milrate$z.avg,y=2,labels=paste0(round(modmed1_milrate$z.avg,5)),pos=3) # ADE
text(x=modmed1_milrate$d.avg,y=3,labels=paste0(round(modmed1_milrate$d.avg,5),'***'),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```

## Hypothesis 3a: The short-term operation of coercive capacity
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed2_milrate=panel_mediate_vcovPL_fixed(model.m = vdem.6b, model.y = vdem.4b,
                                           treat = "ln_popn", mediator = "milrate",
                                           sims = 1000, robustSE = TRUE)
summary(modmed2_milrate)
plot(modmed2_milrate,main="Panel FE, Mediator = milrate, Without Interaction",col="red")
text(x=modmed2_milrate$tau.coef,y=1,labels=paste0(round(modmed2_milrate$tau.coef,5),'**'),pos=3) # ATE
text(x=modmed2_milrate$z.avg,y=2,labels=paste0(round(modmed2_milrate$z.avg,5),'**'),pos=3) # ADE
text(x=modmed2_milrate$d.avg,y=3,labels=paste0(round(modmed2_milrate$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```

## Hypothesis 3b: The conditional operation of coercive capacity
```{r,echo=TRUE,tidy=TRUE}
set.seed(1000)
modmed3=panel_mediate_vcovPL_fixed(model.m = em_milrate, model.y = mo1,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE)
summary(modmed3)
test.modmed(modmed3,
            covariates.1=list(prop_urban=mean(sample.VDem$prop_urban)-sd(sample.VDem$prop_urban)),
            covariates.2=list(prop_urban=mean(sample.VDem$prop_urban)+sd(sample.VDem$prop_urban)),
            sims=1000)
plot(modmed3,main="Pooled OLS, Mediator = milrate, With Interaction",col="red")
text(x=modmed3$tau.coef,y=1,labels=paste0(round(modmed3$tau.coef,5)),pos=3) # ATE
text(x=modmed3$z.avg,y=2,labels=paste0(round(modmed3$z.avg,5)),pos=3) # ADE
text(x=modmed3$d.avg,y=3,labels=paste0(round(modmed3$d.avg,5),'*'),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)

# Additional Mediations
## Less Urban Countries
modmed3.1=panel_mediate_vcovPL_fixed(model.m = em_milrate, model.y = mo1,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE,
                                  covariates = list(prop_urban=mean(sample.VDem$prop_urban)-sd(sample.VDem$prop_urban)))
summary(modmed3.1)

## More Urban Countries
modmed3.2=panel_mediate_vcovPL_fixed(model.m = em_milrate, model.y = mo1,
                                  treat = "ln_popn", mediator = "milrate",
                                  sims = 1000, robustSE = TRUE,
                                  covariates = list(prop_urban=mean(sample.VDem$prop_urban)+sd(sample.VDem$prop_urban)))
summary(modmed3.2)

plot(modmed3.1,main="Pooled OLS, Mediator = milrate, With Interaction (Less Urban)",col="blue")
text(x=modmed3.1$tau.coef,y=1,labels=paste0(round(modmed3.1$tau.coef,5)),pos=3) # ATE
text(x=modmed3.1$z.avg,y=2,labels=paste0(round(modmed3.1$z.avg,5)),pos=3) # ADE
text(x=modmed3.1$d.avg,y=3,labels=paste0(round(modmed3.1$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)

plot(modmed3.2,main="Pooled OLS, Mediator = milrate, With Interaction (More Urban)",col="red")
text(x=modmed3.2$tau.coef,y=1,labels=paste0(round(modmed3.2$tau.coef,5)),pos=3) # ATE
text(x=modmed3.2$z.avg,y=2,labels=paste0(round(modmed3.2$z.avg,5)),pos=3) # ADE
text(x=modmed3.2$d.avg,y=3,labels=paste0(round(modmed3.2$d.avg,5)),pos=3) # ACME
mtext("Note: p<0.001 ***, 0.01 **, 0.05 *",side=1,line=3,cex=1)
```
